---
title: "Practice M1-Bray-Curtis Method"
author: "Lihan"
date: "2021/12/26"
output: html_document
---
### 1.Download all the package

#### Download all the packages I need.
#### 'vegan' is the important one to calculate the abundance.
#### 'gclus','qgraph' can plot the heat map.
#### 'mvabund' provides the data.
#### 'tidyr','dplyr' can sort and filter the data.

```{r}
library(vegan)
library(gclus)
library(qgraph)
library(ggplot2)
library(devtools)
library(mvabund)
library(tidyr)
library(dplyr)
```

### 2.Check and seperate the data

#### We use the data 'tikus', which contains the coral species information in the Tikus island during 1981 ~ 1988, to analyze the difference of abundance between 10 locations.

#### First, I want to seperate the data into 3 years(1981,1983,1985), so I combine 2 dataframe in one and use the variable "time" to filter the data.

#### Next, I add the site information in front of the subsets.

```{r }
data(tikus)
# ?tikus
tikusdat=as.mvabund(tikus$abund)
tikusid=tikus$x
Tikusall=cbind(tikusdat,tikusid)
filtered81 <- filter(Tikusall, time == "81" )
filtered83 <- filter(Tikusall, time == "83" )
filtered85 <- filter(Tikusall, time == "85" )

Site<-c(1,2,3,4,5,6,7,8,9,10)
Fi81=cbind(Site, filtered81)
Fi812=Fi81[,1:76]
Fi83=cbind(Site, filtered83)
Fi832=Fi83[,1:76]
Fi85=cbind(Site, filtered85)
Fi852=Fi85[,1:76]


```

### 3.Bray-Curtis

#### Bray-Curtis (D14) dissimilarity is the golden ditance metric in ecology. We can calculate this with the function 'vegdist' in the package 'vegan'

```{r }
Fi81.dbc <- vegdist(Fi812,"bray")
Fi83.dbc <- vegdist(Fi832,"bray")
Fi85.dbc <- vegdist(Fi852,"bray")
```

### 4.Function

#### It appears that the function 'coldiss' can not work. It's weird but...ok. Instead, I search the original code of it from the website.

#### (https://github.com/JoeyBernhardt/NumericalEcology/blob/master/coldiss.R)

```{r}
"coldiss" <- function(D, nc = 4, byrank = TRUE, diag = FALSE)
{
	require(gclus)

	if (max(D)>1) D <- D/max(D)

	if (byrank) {
		spe.color <- dmat.color(1-D, cm.colors(nc))
	}
	else {
		spe.color <- dmat.color(1-D, byrank=FALSE, cm.colors(nc))
	}

	spe.o <- order.single(1-D)
	speo.color <- spe.color[spe.o, spe.o]
	
	op <- par(mfrow=c(1,2), pty="s")

	if (diag) {
		plotcolors(spe.color, rlabels=attributes(D)$Labels, 
			main="Dissimilarity Matrix", 
			dlabels=attributes(D)$Labels)
		plotcolors(speo.color, rlabels=attributes(D)$Labels[spe.o], 
			main="Ordered Dissimilarity Matrix", 
			dlabels=attributes(D)$Labels[spe.o])
	}
	else {
		plotcolors(spe.color, rlabels=attributes(D)$Labels, 
			main="Dissimilarity Matrix")
		plotcolors(speo.color, rlabels=attributes(D)$Labels[spe.o], 
			main="Ordered Dissimilarity Matrix")
	}

	par(op)
}
```

### 5.Plot

#### The results show the difference between 3 years.
#### The El Nino in 1982 heavily disturbed the area and lead to the decrease of variety.
#### The area seems to recover in 1985.

```{r}
#dissimilarity matrix 
coldiss(Fi81.dbc,byrank=F,diag=T)
coldiss(Fi83.dbc,byrank=F,diag=T)
coldiss(Fi85.dbc,byrank=F,diag=T)
```

```{r}
#network
qgraph(1-Fi81.dbc, layout='spring', vsize=4)
qgraph(1-Fi83.dbc, layout='spring', vsize=4)
qgraph(1-Fi85.dbc, layout='spring', vsize=4)
```
