---
title: "Practice L3"
author: "Lihan"
date: "2021/11/28"
output: html_document
---

### Mission:Fix the code and show two species population growth


#### 1.Load the package first

```{r,  eval=T}
library(animation)
library(ggplot2)
library (gganimate)
```



#### 2.Create the function

Set the growth rate,N1[1] ans N2[1] as variable,other values set same with the wrong code.

I use par() to show two species' plots at same time

```{r,  eval=T}
#start function
grow_n1n2 <- function (growth.rate,nN1,nN2) { 
#setting
  num_gen<-10
  N1 <- rep(0,10)
  N2 <- rep(0,10)
  generation<-1:num_gen
  K1<-100
  K2<-120
  a12<-0.8
  a21<-0.8
  N1[1]<-nN1
  N2[1]<-nN2
  for (i in 2:num_gen) {
    N1[i] = N1[i-1] + (growth.rate* N1[i-1] * ((K1-N1[i-1]-(a12*N2[i-1]))/K1))
    N2[i] = N2[i-1] + (growth.rate* N2[i-1] * ((K2-N2[i-1]-(a21*N1[i-1]))/K2))
    
  }
  par(mfrow=c(1,2))
  plot(N1~generation,type='b', main=paste("N1 Rate =", growth.rate))
  plot(N2~generation,type='b', main=paste("N2 Rate =", growth.rate))
  
}
```

#### 3.Show the difference between rate 0.5 and 1.5

0.5 is similar.

N1's population will go down at 8 generation while N2 will keep go up in rate 1.5 

```{r,  eval=T}
grow_n1n2(0.5,1,1)
grow_n1n2(1.5,1,1)

```

#### 3.1.Show the difference between rate 0.5 and 1.5 with GIF

Try animate!

```{r,  eval=T}
saveGIF({
  for (i in 0.5:1.5){
    grow_n1n2(i,1,1)
  }})

```


#### 4.If there is only one species, how the population growth line will be

If there aren't any other species living at same place, the generation will keep stable at carrying capacities.However, the population will go down while there are other species living with you.

```{r,  eval=T}
grow_n1n2(1.5,1,0)
grow_n1n2(1.5,0,1)
grow_n1n2(1.5,1,1)

```




